%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Research Assistant in Network and System Security Lab} % Job title
    {The School of Computing at Clemson University} % Organization
    {Clemson, SC} % Location
    {May 2018 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item   {\textbf{Network Security}: Research on the Virtualization of Network Intrusion Detection Systems(vNIDS) which is an open source project on GitHub. Implemented RIP, DNS, and HTTP protocol parsers by Binpac, C++ language and PCRE lib, then integrated them into Bro and Click system.}
        \item  {\textbf{System Security}: Research on intrusion and attack of Linux malware. Implemented the parser for bash and python scripts to do static analyze for script files.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Embedded Software Development Intern} % Job title
    {DJI Technology} % Organization
    {Shenzhen, China} % Location
    {Apr. - Nov. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {\textbf{Sensor Driven Development}: Developed more than 10 sensor drivers using C language in the µC/OS system. Validated barometer driver code on MAVIC UAV, a famous unmanned aerial vehicle production.}
        \item {\textbf{Data Analysis}: Collected sensors data to analyze sensors performance with Matlab and Scripts(Bash, Python). Made decisions about which one is the better sensor for product.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Embedded Software Development Intern} % Job title
    {BJ Yunxi Technology} % Organization
    {Guangzhou, China} % Location
    {Jun. 2015 - Apr. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {\textbf{Embedded System}: Designed and implemented a VoIP audio remote control voice terminal software based on OMAP-L138 ARM9, which included logic control, remote system upgrade, hardware initialization, reset examination and SIP user agency initialization.}
        \item  {\textbf{Development Environment}: VoIP server based on Asterisk(Open source application). SIP user agency module based on open source library oSIP and JRTPLIB. Web UI design using GoAhead library.}
        \item  {\textbf{Performance}: VoIP communication system delay time is less than 120ms(Requested:<160ms), and communication quality MOS is 4.8/5.0.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
