%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Projects}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------


  \cventry
    {C++, SDL, XML, Observe Pattern, Singleton Pattern} % Role
    {2-D Game Engine Construction \& Shooting Game (Pirate Captain)} % Project Name
    {Clemson, SC} % Location
    {Sep. - Nov. 2018}  % Date(s) 
    {
      \begin{cvitems} % Description(s)
        \item {Built a 2-D game engine construction used to implement a 2-D game which has a player object, HUD, collision detection, and explosions features with no memory leak and crash.}
        \item {Designed using Data-Driven, constants form an XML file for user easability. In addition, wrote the Object Pool to avoid expensive acquisition and release of game resources by recycling objects that are no longer in use.}
        \item {Using C++ and SDL2.0 as the technology stack. Various design patterns were used, such as singleton, factory, object pool, observer, flyweight, strategy.}
      \end{cvitems}
    }

  \cventry
    {Python 2.7, AWS, MapReduce, IFTTT, Telegram} % Role
    {Predictor for the Trend of Bitcoin Price based on LSTM Neural Network and AWS} % Project Name
    {Clemson, SC} % Location
    {Sep. - Nov. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Utilized sentiment analysis and LSTM neural network to create a Bitcoin price predictor.}
        \item {The predictor can forecast the trend of Bitcoin price, then send message to user's smart device by IFTTT webhook service, and Telegram client.}
      \end{cvitems}
    }


  \cventry
    {C++, Python 2.7, Flex, Bison, Visitor Pattern, Singleton Pattern} % Role
    {A Mini Python Interpreter} % Project Name
    {Clemson, SC} % Location
    {Sep. - Nov. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Implemented a mini interpreter for Python 2.7 with C++ 11, which can interpret some basic sentences. The scanner and parser are implemented based on Flex and Bison.}
        \item {Designed and developed the interpreter based on Object Orientated thinking, singleton, visitor pattern, which are used to implement the abstract syntax tree, symbol table and basic operations.}
        \item {Performance has been demonstrated as good as Python 2.7 and can save 30\% of time for short python source code.}
      \end{cvitems}
    }


%   \cventry
%     {Python 2.7, AWS, MapReduce, IFTTT, Telegram} % Role
%     {A deep Learning-Based Online Network Intrusion Detection System} % Project Name
%     {Clemson, SC} % Location
%     {Sep. - Nov. 2018} % Date(s)
%     {
%       \begin{cvitems} % Description(s)
%         \item {Run Kitsune in local network.}
%         \item {Generate adversarial attacks.}
%         \item {Test and evaluate this attack.}
%       \end{cvitems}
%     }

 
  \cventry
    {C++, Binpac language, Click System, Bro System} % Role
    {Network Protocol Parser} % Project Name
    {Clemson, SC} % Location
    {May - Aug. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item  {Design the RIP, DNS and HTTP network protocol parsers by C++ and Binpac language.}
        \item {Implemented these network protocol parser based on the Binpac and Open PCRE lib. As a result, it is easily integrated into the other project. For instance, I had integrated it into Bro and Click system in this project.}
      \end{cvitems}
    }

  \cventry
    {Python 3.5, Tkinter, MVC Design Pattern} % Role
    {Paper Tracking Application} % Project Name
    {Clemson, SC} % Location
    {May - Aug. 2018}% Date(s)
    {
      \begin{cvitems} % Description(s)
        \item{Designed Paper Tracking Application which can manage the importance, urgency and tags of the papers. Developed GUI by Tkinter python library. Implemented the paper manager code(Python 3.5) using MVC Design Pattern.}
        \item {Applied technology: Tkinter, Python 3.5, MVC Design Pattern.}
      \end{cvitems}
    }

  \cventry
    {C, SIP, RTP, VoIP, ARC} % Role
    {VolP Audio Remote Control System Based on SIP Protocol} % Project Name
    {Guangzhou, China} % Location
    {Sep. 2015 - Jun. 2016}% Date(s)
    {
      \begin{cvitems} % Description(s)
        \item  {Designed and implemented a VoIP audio remote control voice terminal software which included main control module, based on OMAP-L138 ARM9 chip.}
        \item {Implements VoIP audio control application, Main control module with logic control, hardware initialization, reset examination and SIP user agency initialization.}
        \item  {Implemented SIP user agency module which includes three things: SIP communication module, RTP transmission module, and a WEB configuration module.}
        \item {Implemented SIP protocol stack by oSIP open lib, RTP protocol stack by JRTPLib, and WEB server by GoAhead.}
        \item {Test result: VoIP communication system delay time is less than 120ms, and system language communication quality MOS is 4.8.}
      \end{cvitems}
    }

  \cventry
    {C, ARM, UART, I2C, SPI} % Role
    {2015 RoboMaster Robot Competition} % Project Name
    {Shenzheng, China} % Location
    {Sep. 2014 - Jun. 2015}% Date(s)
    {
      \begin{cvitems} % Description(s)
        \item  {Finished STM32F4 communication with a remote pan and adjustment of PID parameters.}
        \item {Worked out main Control Board receives remote control data error after adding the door dog.}
      \end{cvitems}
    }

  \cventry
    {C++, GCC, QT, Shell Script, eCryptfs} % Role
    {An Encrypted File system Based on Linux} % Project Name
    {Hefei, China} % Location
    {2014 - 2015}% Date(s)
    {
      \begin{cvitems} % Description(s)
        \item  {Realized eCryptfs cryptographic file system implementation mechanism, and designed UI Interface based on QT, dealt with root permissions file access vulnerability.}
        \item  {Designed team work plan and the overall framework of the project. Finished this project perfectly and got the second prize of USTC Software Design competition(Top 5\%).}
      \end{cvitems}
    }

%   \cventry
%     {PLC} % Role
%     {Physical Simulation Platform for Control of the Natural Circulation Boiler} % Project Name
%     {Kunming, China} % Location
%     {Sep. 2013 - Jul. 2014}% Date(s)
%     {
%       \begin{cvitems} % Description(s)
%         \item  {Designed team work plan and the overall framework of the project.}
%         \item  {Realized eCryptfs cryptographic file system implementation mechanism, designed UI Interface based on QT, dealt with root permissions file access vulnerability. }
%         \item  {Applied technology: QT Development, Linux file system, GCC, Makefile, and gdb.}
%         \item  {Finished perfectly and got second prize of USTC.} 
%       \end{cvitems}
%     }

%---------------------------------------------------------
\end{cventries}
