
%-----------EXPERIENCE-----------------
\section{Related Experience}
  \subItemListStart
    %---05/2018 Research Assistant at Clemson University
    \experienceSubItem
      {The School of Computing at Clemson University}{May 2018 - Present}
      {Research Assistant in Network and System Security Lab}{Clemson, SC}
      
      \detailItemListStart
        \detailItem{Network Security}
          {Research on the Virtualization of Network Intrusion Detection Systems(vNIDS). Implemented RIP, DNS, and HTTP protocol parsers by Binpac, C++ language and PCRE lib, then integrated them into Bro and Click system.}
        \detailItem{System Security}
          {Research on intrusion and attack of Linux malware. Implemented the parser for bash and python scripts to do static analyze for script files.}
      \detailItemListEnd

    %---04/2016- 11/2016 DJI: Embedded Software Development Intern
    \experienceSubItem
      {DJI Technology}{Apr. - Nov. 2016}
      {Embedded Software Development Intern}{Shenzhen, China}
      \detailItemListStart
        \detailItem{Sensor Driven Development}
          {Developed more than 10 sensor drivers using C language in the µC/OS system. Validated barometer driver code on MAVIC UAV, a famous unmanned aerial vehicle production.}
        \detailItem{Data Analysis}
          {Collected sensors data to analyze sensors performance with Matlab and Scripts(Bash, Python). Made decisions about which one is the better sensor for product.}
        %   {Accomplished the c code to  IIC, UART, SPI protocol  the c code to collect the sensor data for more than ten sensors.}
      \detailItemListEnd
    
    %---07/2015- 04/2016 Yunxi: Embedded Software Development Intern
    \experienceSubItem
      {BJ Yunxi Technology}{Jun. 2015 - Apr. 2016}
      {Embedded Software Development Intern}{Guangzhou, China}
      \detailItemListStart
        \detailItem{Embedded System}
          {Designed and implemented a VoIP audio remote control voice terminal software based on OMAP-L138 ARM9, which included logic control, remote system upgrade, hardware initialization, reset examination and SIP user agency initialization.}
        \detailItem{Development Environment}
          {VoIP server based on Asterisk(Open source application). SIP user agency module based on open source library oSIP and JRTPLIB. Web UI design using GoAhead library.}
         \detailItem{Performance}
          {VoIP communication system delay time is less than 120ms(Requested:<160ms), and communication quality MOS is 4.8/5.0.}

      \detailItemListEnd
  \subItemListEnd
